---
title: "Scatterpolot_Graph_R"
author: "Dylan CASSIDY"
date: '2022-03-16'
output: "output=github_document"
---

# Call libraries ggplot & data.table
# Use fread to Import Data from Excel Sheet
# Drop first column
```{r}
library(ggplot2)
library(data.table)
dt <- fread("~/Github Projects/Scatterplot R/Economist_Corruption_Data.csv", drop=1)

head(dt)
```

#Set up scatterplot using X-axis for CPI and y-axis for HDI
#Color set by region
```{r}
pl <- ggplot(dt, aes(x=CPI,y=HDI,color=Region)) + geom_point(shape=19, size=3)

pl
```

# Change shape of scatterplot to large empty circles
```{r}
pl2 <- ggplot(dt, aes(x=CPI,y=HDI,color=Region)) + geom_point(shape=1, size=4)

pl2
```

# Add simple red trend line using geom_smooth.
```{r}
pl3 <- pl2 + geom_smooth(method="lm",formula=y~log(x),se=FALSE,color='blue')

pl3
```

# Add labels to the scatterplot, using country name as label
```{r}
pl4 <- pl3 + geom_text(aes(label=Country))

pl4
```

# Limit labels to specific countries of interest
# Assign desired countries to 'pointsToLabel', then use geom_text to put these on the scatterplot
```{r}
pointsToLabel <- c("Russia", "Venezuela", "Iraq", "Myanmar", "Sudan",
                   "Afghanistan", "Congo", "Greece", "Argentina", "Brazil",
                   "India", "Italy", "China", "South Africa", "Spane",
                   "Botswana", "Cape Verde", "Bhutan", "Rwanda", "France",
                   "United States", "Germany", "Britain", "Barbados", "Norway", "Japan",
                   "New Zealand", "Singapore")


pl4 <- pl3 + geom_text(aes(label = Country), color = "gray20", 
                data = subset(dt, Country %in% pointsToLabel),check_overlap = TRUE)

pl4
```


# Add bw theme so that background is clear
```{r}
library(ggthemes)

pl5 <- pl4 + theme_economist_white()

pl5
```

# Set x-axis details
```{r}
pl6 <- pl5 + scale_x_continuous(name='Corruption Perceptions Index, 2011 (10=least corrupt)', breaks=1:10)

pl6
```

# Set y-axis details
```{r}
pl7 <- pl6 + scale_y_continuous(name='Human Development Index, 2011 (1=Best)', waiver())

pl7

```

# Set title
# View finished plot
```{r}
pl8 <- pl7 + ggtitle('Corruption and Human Development')

pl8

```
